Supplementary material

### 2017-10-03 Manuscript/ms.tex
Place-holder figures in ms

Questions:
\begin{itemize}
\item How wells does the model fit the case reports and mosquito surveillance data?
\item What do the estimated time series of demographic rates look like? How smooth are they? How strong is the periodic signal relative to noise?
\item How do peaks in $\psi$ line up with peaks in $q_t$?
\item How effective is control informed by $\psi$ compared to control informed by $q_t$?
\end{itemize}

@@

>>>>

@@

\begin{figure}[!h]
%\includegraphics[angle = 270, scale = 1]{figures/fig1.eps}
\caption{{\bf Estimated latent birth and death rates.}
}
\label{latent}
\end{figure}

\begin{figure}[!h]
%\includegraphics[angle = 270, scale = 1]{figures/fig1.eps}
\caption{{\bf Cases prevented by adult control.}
}
\label{adultcontrol}
\end{figure}
